---
title: "The Cytokine in Pregnancy Database"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    self_contained: false
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(ggrepel)
library(plotly)
library(DT)
library(meta)
source("R/load_data.R")
source("R/plot_stat.R")
source("R/export_data.R")
source("R/estimateEffect.R")
```

# Overview {data-icon="fa-home"}

## Row

### Studies

```{r}
valueBox(nrow(df_studies), icon = "fa-file-alt")
```

### Aggregated data points

```{r}
valueBox(nrow(df_aggregated), icon = "fa-filter")
```

### Raw data points

```{r}
valueBox(nrow(df_raw), icon = "fa-chart-bar")
```

### Participants

```{r}
valueBox(sum(df_studies$ntot), icon = "fa-female")
```

### Different cytokines

```{r}
valueBox(nrow(cytokines), icon = "fa-snowflake")
```

## Row

### Studies

```{r}
datatable(df_studies[,c("author","year","title","doi","design","type")], class = 'cell-border stripe')
```

### Usage {data-width="150"}

Download

-   [Aggregated data](./aggregated_data.csv)
-   [Raw data](./aggregated_data.csv)

License:

Citation:

# Details {data-icon="fa-info"}

## Row

### Aggregated

```{r}
df_aggregated_summarized <- aggregate(data = merge(df_aggregated, cytokines), value ~ author + title + condition + printname, FUN = length)
datatable(df_aggregated_summarized, class = 'cell-border stripe', rownames = FALSE)
```

### Aggregated

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines), aes(printname)) + geom_bar() + 
    theme_bw() + 
    labs(x = "Cytokine", y = "Number of observations") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
)

#ggplot(df_aggregated, aes(ga_days.mean, value, group = filename)) + geom_point() + geom_line() + facet_wrap(~cytokine, scales = "free") + theme_bw()
```

## Row

### Raw

```{r}
#ggplot(merge(df_aggregated,cytokines), aes(printname)) + geom_bar() + 
#  theme_bw() + 
#  labs(x = "Cytokine", y = "Number of observations") + 
#  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# Conditions {data-icon="fa-chart-pie"}

## Row

### Tanger책s (2015)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Tanger책s")
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

### Arikan (2012)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Arikan")
df_plot$condition <- paste(df_plot$condition, df_plot$condition.severity)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy ")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

## Row

### Garcia (2018)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Garcia")
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

### Cheslack-Postava (2016)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Cheslack-Postava")
df_plot$condition <- paste0(df_plot$ga.string,", ",df_plot$condition)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "First trimester, healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

## Row

### Taylor (2016)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Taylor")
df_plot$condition <- paste0(df_plot$ga.string,", ",df_plot$condition)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "First trimester, healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

### Szarka (2010)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Szarka")
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

## Row

### Aggarwal (2019)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Aggarwal")
df_plot$condition <- paste0(df_plot$ga.string, ", ", df_plot$condition)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == unique(df_plot$condition)[1])$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig
```

### Cui (2017)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Cui")
df_plot$condition <- paste0(df_plot$condition, ", ",df_plot$condition.severity)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy, ")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

## Row

### Braga (2019)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Braga")
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

### Georgiou (2011)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Georgiou")
df_plot$condition <- paste0(df_plot$condition, ", week ",df_plot$ga.week.median)
df_plot <- subset(df_plot, cytokine %in% cytokine[value > 0 & condition == "healthy, week 7"])
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy, week 7")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```


# Conditions {data-icon="fa-heartbeat"}

## Row

### Tanger책s (2015)

```{r}

df_plot <- subset(df_aggregated, author == "Tanger책s")
diffPlot(df_plot, refLevel = "healthy")

```

### Arikan (2012)

```{r}

df_plot <- subset(df_aggregated, author == "Arikan")
df_plot$condition <- paste(df_plot$condition, df_plot$condition.severity)
diffPlot(df_plot, refLevel = "healthy ")

```

## Row

### Garcia (2018)

```{r}

df_plot <- subset(df_aggregated, author == "Garcia")
diffPlot(df_plot, refLevel = "healthy")

```

### Cheslack-Postava (2016)

```{r}

df_plot <- subset(df_aggregated, author == "Cheslack-Postava")
df_plot$condition <- paste0(df_plot$ga.string,", ",df_plot$condition)
diffPlot(df_plot, refLevel = "First trimester, healthy")

```

## Row

### Taylor (2016)

```{r}

df_plot <- subset(df_aggregated, author == "Taylor")
df_plot$condition <- paste0(df_plot$ga.string,", ",df_plot$condition)
diffPlot(df_plot, refLevel = "First trimester, healthy")
```

### Szarka (2010)

```{r}

df_plot <- subset(df_aggregated, author == "Szarka")
diffPlot(df_plot, refLevel = "healthy")

```

## Row

### Aggarwal (2019)

```{r}

df_plot <- subset(df_aggregated, author == "Aggarwal")
df_plot$condition <- paste0(df_plot$ga.string, ", ", df_plot$condition)
diffPlot(df_plot, refLevel = unique(df_plot$condition[1]))

```

### Cui (2017)

```{r}

df_plot <- subset(df_aggregated, author == "Cui")
df_plot$condition <- paste0(df_plot$condition, ", ",df_plot$condition.severity)
diffPlot(df_plot, refLevel = "healthy, ")

```

## Row

### Braga (2019)

```{r}

df_plot <- subset(df_aggregated, author == "Braga")
diffPlot(df_plot, refLevel = "healthy")

```

### Georgiou (2011)

```{r}

df_plot <- subset(df_aggregated, author == "Georgiou")
df_plot$condition <- paste0(df_plot$condition, ", week ",df_plot$ga.week.median)
df_plot <- subset(df_plot, cytokine %in% cytokine[value > 0 & condition == "healthy, week 7"])
diffPlot(df_plot, refLevel = "healthy, week 7")

```



# Meta-analysis {data-icon="fa-sitemap"}

## Row

### Preeclampsia: IL-6

Please note that trimesters are pooled at the moment and that the results are likely to change when the trimesters are assessed separately.


```{r, out.height="100%", out.width="100%", fig.width=16, fig.height=8}
df_meta <- subset(df_aggregated, cytokine == "IL_6" & is.na(subgroup) & condition %in% c("healthy", "preeclampsia"))
df_meta_prep <- data.frame()
df_meta$id <- paste(df_meta$author, df_meta$title)
df_meta$aut <- paste0(df_meta$author, " et al. (", df_meta$year, ")")
for(i in unique(df_meta$id)){
  for(j in unique(df_meta$ga.string[df_meta$id == i])){
    if(any(subset(df_meta, id == i & ga.string == j)$condition == "preeclampsia")){
      df_meta_prep <- rbind(
        df_meta_prep,
        prep_meta(
          dff = subset(df_meta, id == i & ga.string == j),
          Author = subset(df_meta, id == i & ga.string == j)$aut[1],
          c = "healthy",
          e = "preeclampsia"
        )
      )
    }
  }
}

m.cont <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = df_meta_prep,
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "IL-6")


png(file = "forestplot_IL_6.png", width = 3200, height = 2000, res = 300)
forest.meta(m.cont, 
            sortvar = TE,
            predict = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "g", "SE"))
dev.off()


m.cont_nona <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = subset(df_meta_prep, !is.na(ga)),
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "IL-6")
m.reg <- metareg(m.cont_nona, ~ga)
png(file = "bubbleplot_IL_6.png", width = 3200, height = 2000, res = 300)
bubble(m.reg, studlab = TRUE)
dev.off()

```

## Row

### Preeclampsia: IFN-g

```{r, out.height="100%", out.width="100%", fig.width=16, fig.height=8}
df_meta <- subset(df_aggregated, cytokine == "IFN_g" & is.na(subgroup) & condition %in% c("healthy", "preeclampsia"))
df_meta_prep <- data.frame()
df_meta$id <- paste(df_meta$author, df_meta$title)
df_meta$aut <- paste0(df_meta$author, " et al. (", df_meta$year, ")")
for(i in unique(df_meta$id)){
  for(j in unique(df_meta$ga.string[df_meta$id == i])){
    if(any(subset(df_meta, id == i & ga.string == j)$condition == "preeclampsia")){
      df_meta_prep <- rbind(
        df_meta_prep,
        prep_meta(
          dff = subset(df_meta, id == i & ga.string == j),
          Author = subset(df_meta, id == i & ga.string == j)$aut[1],
          c = "healthy",
          e = "preeclampsia"
        )
      )
    }
  }
}

m.cont <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = df_meta_prep,
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "IFN-g")


forest.meta(m.cont, 
            sortvar = TE,
            predict = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "g", "SE"))

m.cont_nona <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = subset(df_meta_prep, !is.na(ga)),
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "IFN-g")
m.reg <- metareg(m.cont_nona, ~ga)
bubble(m.reg, studlab = TRUE)
```

## Row

### Preeclampsia: IL-10

```{r, out.height="100%", out.width="100%", fig.width=16, fig.height=8}
df_meta <- subset(df_aggregated, cytokine == "IL_10" & is.na(subgroup) & condition %in% c("healthy", "preeclampsia"))
df_meta_prep <- data.frame()
df_meta$id <- paste(df_meta$author, df_meta$title)
df_meta$aut <- paste0(df_meta$author, " et al. (", df_meta$year, ")")
for(i in unique(df_meta$id)){
  for(j in unique(df_meta$ga.string[df_meta$id == i])){
    if(any(subset(df_meta, id == i & ga.string == j)$condition == "preeclampsia")){
      df_meta_prep <- rbind(
        df_meta_prep,
        prep_meta(
          dff = subset(df_meta, id == i & ga.string == j),
          Author = subset(df_meta, id == i & ga.string == j)$aut[1],
          c = "healthy",
          e = "preeclampsia"
        )
      )
    }
  }
}

m.cont <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = df_meta_prep,
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "IL-10")


forest.meta(m.cont, 
            sortvar = TE,
            predict = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "g", "SE"))

m.cont_nona <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = subset(df_meta_prep, !is.na(ga)),
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "IL-10")
m.reg <- metareg(m.cont_nona, ~ga)
bubble(m.reg, studlab = TRUE)

```


## Row

### Preeclampsia: CRP

```{r, out.height="100%", out.width="100%", fig.width=16, fig.height=8}
df_meta <- subset(df_aggregated, cytokine == "CRP" & is.na(subgroup) & condition %in% c("healthy", "preeclampsia"))
df_meta_prep <- data.frame()
df_meta$id <- paste(df_meta$author, df_meta$title)
df_meta$aut <- paste0(df_meta$author, " et al. (", df_meta$year, ")")
for(i in unique(df_meta$id)){
  for(j in unique(df_meta$ga.string[df_meta$id == i])){
    if(any(subset(df_meta, id == i & ga.string == j)$condition == "preeclampsia")){
      df_meta_prep <- rbind(
        df_meta_prep,
        prep_meta(
          dff = subset(df_meta, id == i & ga.string == j),
          Author = subset(df_meta, id == i & ga.string == j)$aut[1],
          c = "healthy",
          e = "preeclampsia"
        )
      )
    }
  }
}

m.cont <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = df_meta_prep,
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "CRP")

png(file = "forestplot_CRP.png", width = 3200, height = 2000, res = 300)
forest.meta(m.cont, 
            sortvar = TE,
            predict = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "g", "SE"))
dev.off()

m.cont_nona <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = subset(df_meta_prep, !is.na(ga)),
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "CRP")
m.reg <- metareg(m.cont_nona, ~ga)

png(file = "bubbleplot_CRP.png", width = 3200, height = 2000, res = 300)
bubble(m.reg, studlab = TRUE)
dev.off()
```

## Row

### Preeclampsia: IL-8

```{r, out.height="100%", out.width="100%", fig.width=16, fig.height=8}
df_meta <- subset(df_aggregated, cytokine == "IL_8" & is.na(subgroup) & condition %in% c("healthy", "preeclampsia"))
df_meta_prep <- data.frame()
df_meta$id <- paste(df_meta$author, df_meta$title)
df_meta$aut <- paste0(df_meta$author, " et al. (", df_meta$year, ")")
for(i in unique(df_meta$id)){
  for(j in unique(df_meta$ga.string[df_meta$id == i])){
    if(any(subset(df_meta, id == i & ga.string == j)$condition == "preeclampsia")){
      df_meta_prep <- rbind(
        df_meta_prep,
        prep_meta(
          dff = subset(df_meta, id == i & ga.string == j),
          #Author = subset(df_meta, id == i & ga.string == j)$aut[1],
          c = "healthy",
          e = "preeclampsia"
        )
      )
    }
  }
}

m.cont <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = df_meta_prep,
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "IL-8")

png(file = "forestplot_IL_8.png", width = 3200, height = 2000, res = 300)
forest.meta(m.cont, 
            sortvar = TE,
            predict = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "g", "SE"))
dev.off()

m.cont_nona <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = subset(df_meta_prep, !is.na(ga)),
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "IL-8")
m.reg <- metareg(m.cont_nona, ~ga)

png(file = "bubbleplot_IL_8.png", width = 3200, height = 2000, res = 300)
bubble(m.reg, studlab = TRUE)
dev.off()

```

## Row

### Preeclampsia: TNF-a

```{r, out.height="100%", out.width="100%", fig.width=16, fig.height=8}
df_meta <- subset(df_aggregated, cytokine == "TNF_a" & is.na(subgroup) & condition %in% c("healthy", "preeclampsia"))
df_meta_prep <- data.frame()
df_meta$id <- paste(df_meta$author, df_meta$title)
df_meta$aut <- paste0(df_meta$author, " et al. (", df_meta$year, ")")
for(i in unique(df_meta$id)){
  for(j in unique(df_meta$ga.string[df_meta$id == i])){
    if(any(subset(df_meta, id == i & ga.string == j)$condition == "preeclampsia")){
      print(subset(df_meta, id == i & ga.string == j)$aut)
      df_meta_prep <- rbind(
        df_meta_prep,
        prep_meta(
          dff = subset(df_meta, id == i & ga.string == j),
          Author = subset(df_meta, id == i & ga.string == j)$aut[1],
          c = "healthy",
          e = "preeclampsia"
        )
      )
    }
  }
}

m.cont <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = df_meta_prep,
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "TNF-a")

png(file = "forestplot_TNF_a.png", width = 3200, height = 2000, res = 300)
forest.meta(m.cont, 
            sortvar = TE,
            predict = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "g", "SE"))
dev.off()

m.cont_nona <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = subset(df_meta_prep, !is.na(ga) & Author != "Ma et al. (2019)"),
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "TNF-a")
m.reg <- metareg(m.cont_nona, ~ga)
png(file = "bubbleplot_TNF_a.png", width = 3200, height = 2000, res = 300)
bubble(m.reg, studlab = TRUE)
dev.off()

```


## Row

### Preeclampsia: IL-1b

```{r, out.height="100%", out.width="100%", fig.width=16, fig.height=8}
df_meta <- subset(df_aggregated, cytokine == "IL_1b" & is.na(subgroup) & condition %in% c("healthy", "preeclampsia"))
df_meta_prep <- data.frame()
df_meta$id <- paste(df_meta$author, df_meta$title)
df_meta$aut <- paste0(df_meta$author, " et al. (", df_meta$year, ")")
for(i in unique(df_meta$id)){
  for(j in unique(df_meta$ga.string[df_meta$id == i])){
    if(any(subset(df_meta, id == i & ga.string == j)$condition == "preeclampsia")){
      df_meta_prep <- rbind(
        df_meta_prep,
        prep_meta(
          dff = subset(df_meta, id == i & ga.string == j),
          Author = subset(df_meta, id == i & ga.string == j)$aut[1],
          c = "healthy",
          e = "preeclampsia"
        )
      )
    }
  }
}

m.cont <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = df_meta_prep,
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "TNF-a")


forest.meta(m.cont, 
            sortvar = TE,
            predict = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "g", "SE"))

m.cont_nona <- metacont(
  median.e = median.e, 
  median.c = median.c,
  mean.e = mean.e, 
  mean.c = mean.c,
  q1.c = q1.c, q1.e = q1.e, 
  q3.c = q3.c, q3.e = q3.e,
  min.c = min.c, min.e = min.e, 
  max.c = max.c, max.e = max.e,
  sd.e = sd.e, sd.c = sd.c, 
  n.e = n.e, n.c = n.c, 
  studlab = Author,
  data = subset(df_meta_prep, !is.na(ga) & Author != "Ma et al. (2019)"),
  sm = "SMD",
  method.smd = "Hedges",
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  title = "IL-1b")
m.reg <- metareg(m.cont_nona, ~ga)
bubble(m.reg, studlab = TRUE)

```

# Trends {data-icon="fa-chart-line"}

## Row {.tabset data-height=900}

### Method

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = method)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Method") + 
    facet_wrap(~printname)
)
```

### Tissue

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = tissue)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Tissue") + 
    facet_wrap(~printname)
)
```

### BMI

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = ifelse(is.na(bmi), bmi.baseline, bmi))) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "BMI") + 
    facet_wrap(~printname)
)
```

### Maternal age

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = age)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Maternal age") + 
    facet_wrap(~printname)
)
```

### Systolic blood pressure

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = systolic)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Systolic blood pressure") + 
    facet_wrap(~printname)
)
```

### Distolic blood pressure

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = diastolic)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Distolic blood pressure") + 
    facet_wrap(~printname)
)
```

# Contribute {data-icon="fa-hands-helping"}

## Row

### How to contribute

Feel free to contribute! The easiest way to contribute is through [github](https://github.com/andjar/CyPreg) and is described step-wise below.

1.  If you are new to git, [this guide](https://www.dataschool.io/how-to-contribute-on-github/) can help you getting started. The repository for the database is `https://github.com/andjar/CyPreg.git`

2.  Check `data/studies.csv` (or the Overview page) to see that the study you want to add is missing from the database

3.  Add the new study to `data/studies.csv`. Here, `type` should be either `raw` or `aggregated`, and the preferred filename is of the form `firstauthorYYYY.csv` (e.g. `stokkeland2019.csv`)

4.  The data are to be added in a new .csv-file but it may be nice to use an existing file as template. Raw data live in the `data/raw` folder and aggregated data in `data/aggregated`.

5.  The data file should have a long format where each cytokine measurement has its own row. The variable names are columns with the variable name on top. Please see `data/variables.csv` for variable names

    -   If you want to append a new variable, you must also add it to `data/variables.csv` and provide a short description so that others can understand exactly what it means

    -   Please adhere to the following convention: Variable names should have the form `basename.suffix` where `basename` is added to `data/variable.csv`. Available suffixes, that are used in the csf files that contain data, are

        -   `median`: If the given value is reported as median

        -   `mean`: If the given value is reported as mean
        
        -   `sd`: If the variation in the given value is reported as standard deviation
        
        -   `percentile.%n`: If the variation in the given value is reported as the %nth percentile. Remember that range corresponds to the 0-100th percentile
        
        -   `def`: To provide details regarding a basevariable

    -   The highest and lower percentiles will be used for `basename.upper` and `basename.lower`, respectively. If standard deviation is given, upper and lower will be the corresponding value +/- 1.97 times the standard deviation

6.  Cytokine names should match the column `cytokine` in `data/cytokines.csv`