---
title: "The Cytokine in Pregnancy Database"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    self_contained: false
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(ggrepel)
library(plotly)
library(DT)
source("R/load_data.R")
source("R/plot_stat.R")
source("R/export_data.R")
diffPlot <- function(df_plot, refLevel = "healthy"){
  tmp <- Reduce(rbind, lapply(unique(df_plot$condition), function(i){
    Reduce(rbind, lapply(unique(df_plot$cytokine[df_plot$condition == i]), function(x){
      data.frame(
       cytokine = x,
       diff = (subset(df_plot, condition == i & cytokine == x)$value-subset(df_plot, condition == refLevel & cytokine == x)$value)/subset(df_plot, condition == refLevel & cytokine == x)$value,
       condition = i
      )
    }))
  }))
  tmp <- subset(tmp, condition != refLevel)
  tmp$cytokine <- factor(tmp$cytokine, levels = unique(tmp$cytokine)[order(subset(tmp, condition == tmp$condition[1])$diff)])
return(
  ggplotly(
    ggplot(tmp, aes(cytokine, 100*diff, color = condition)) + 
      geom_segment( aes(xend=cytokine, y=0, yend=100*diff)) + 
      geom_point() + theme_bw() + coord_flip() + 
      facet_wrap(~condition) + theme(legend.position = "none") +
      labs(y = paste0("Deviation from ", refLevel, " [%]"), x = "Cytokine")
  )
)
}
```

# Overview {data-icon="fa-home"}

## Row

### Studies

```{r}
valueBox(nrow(df_studies), icon = "fa-file-alt")
```

### Aggregated data points

```{r}
valueBox(nrow(df_aggregated), icon = "fa-filter")
```

### Raw data points

```{r}
valueBox(nrow(df_raw), icon = "fa-chart-bar")
```

### Participants

```{r}
valueBox(sum(df_studies$ntot), icon = "fa-female")
```

### Different cytokines

```{r}
valueBox(nrow(cytokines), icon = "fa-snowflake")
```

## Row

### Studies

```{r}
datatable(df_studies[,c("author","year","title","doi","design","type")], class = 'cell-border stripe')
```

### Usage {data-width="150"}

Download

-   [Aggregated data](./aggregated_data.csv)
-   [Raw data](./aggregated_data.csv)

License:

Citation:

# Details {data-icon="fa-info"}

## Row

### Aggregated

```{r}
df_aggregated_summarized <- aggregate(data = merge(df_aggregated, cytokines), value ~ author + title + condition + printname, FUN = length)
datatable(df_aggregated_summarized, class = 'cell-border stripe', rownames = FALSE)
```

### Aggregated

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines), aes(printname)) + geom_bar() + 
    theme_bw() + 
    labs(x = "Cytokine", y = "Number of observations") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
)

#ggplot(df_aggregated, aes(ga_days.mean, value, group = filename)) + geom_point() + geom_line() + facet_wrap(~cytokine, scales = "free") + theme_bw()
```

## Row

### Raw

```{r}
#ggplot(merge(df_aggregated,cytokines), aes(printname)) + geom_bar() + 
#  theme_bw() + 
#  labs(x = "Cytokine", y = "Number of observations") + 
#  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# Conditions {data-icon="fa-chart-pie"}

## Row

### Tanger책s (2015)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Tanger책s")
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

### Arikan (2012)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Arikan")
df_plot$condition <- paste(df_plot$condition, df_plot$condition.severity)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy ")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

## Row

### Garcia (2018)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Garcia")
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

### Cheslack-Postava (2016)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Cheslack-Postava")
df_plot$condition <- paste0(df_plot$ga.string,", ",df_plot$condition)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "First trimester, healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

## Row

### Taylor (2016)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Taylor")
df_plot$condition <- paste0(df_plot$ga.string,", ",df_plot$condition)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "First trimester, healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

### Szarka (2010)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Szarka")
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

## Row

### Aggarwal (2019)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Aggarwal")
df_plot$condition <- paste0(df_plot$ga.string, ", ", df_plot$condition)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == unique(df_plot$condition)[1])$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig
```

### Cui (2017)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Cui")
df_plot$condition <- paste0(df_plot$condition, ", ",df_plot$condition.severity)
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy, ")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

## Row

### Braga (2019)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Braga")
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```

### Georgiou (2011)

```{r}
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  )
df_plot <- subset(df_aggregated, author == "Georgiou")
df_plot$condition <- paste0(df_plot$condition, ", week ",df_plot$ga.week.median)
df_plot <- subset(df_plot, cytokine %in% cytokine[value > 0 & condition == "healthy, week 7"])
for(i in unique(df_plot$condition)){
  fig <- fig %>%
  add_trace(
    r = subset(df_plot, condition == i)$value/subset(df_plot, condition == "healthy, week 7")$value,
    theta = subset(df_plot, condition == i)$cytokine,
    name = i
  )
}

fig

```


# Conditions {data-icon="fa-heartbeat"}

## Row

### Tanger책s (2015)

```{r}

df_plot <- subset(df_aggregated, author == "Tanger책s")
diffPlot(df_plot, refLevel = "healthy")

```

### Arikan (2012)

```{r}

df_plot <- subset(df_aggregated, author == "Arikan")
df_plot$condition <- paste(df_plot$condition, df_plot$condition.severity)
diffPlot(df_plot, refLevel = "healthy ")

```

## Row

### Garcia (2018)

```{r}

df_plot <- subset(df_aggregated, author == "Garcia")
diffPlot(df_plot, refLevel = "healthy")

```

### Cheslack-Postava (2016)

```{r}

df_plot <- subset(df_aggregated, author == "Cheslack-Postava")
df_plot$condition <- paste0(df_plot$ga.string,", ",df_plot$condition)
diffPlot(df_plot, refLevel = "First trimester, healthy")

```

## Row

### Taylor (2016)

```{r}

df_plot <- subset(df_aggregated, author == "Taylor")
df_plot$condition <- paste0(df_plot$ga.string,", ",df_plot$condition)
diffPlot(df_plot, refLevel = "First trimester, healthy")
```

### Szarka (2010)

```{r}

df_plot <- subset(df_aggregated, author == "Szarka")
diffPlot(df_plot, refLevel = "healthy")

```

## Row

### Aggarwal (2019)

```{r}

df_plot <- subset(df_aggregated, author == "Aggarwal")
df_plot$condition <- paste0(df_plot$ga.string, ", ", df_plot$condition)
diffPlot(df_plot, refLevel = unique(df_plot$condition[1]))

```

### Cui (2017)

```{r}

df_plot <- subset(df_aggregated, author == "Cui")
df_plot$condition <- paste0(df_plot$condition, ", ",df_plot$condition.severity)
diffPlot(df_plot, refLevel = "healthy, ")

```

## Row

### Braga (2019)

```{r}

df_plot <- subset(df_aggregated, author == "Braga")
diffPlot(df_plot, refLevel = "healthy")

```

### Georgiou (2011)

```{r}

df_plot <- subset(df_aggregated, author == "Georgiou")
df_plot$condition <- paste0(df_plot$condition, ", week ",df_plot$ga.week.median)
df_plot <- subset(df_plot, cytokine %in% cytokine[value > 0 & condition == "healthy, week 7"])
diffPlot(df_plot, refLevel = "healthy, week 7")

```


# Trends {data-icon="fa-chart-line"}

## Row {.tabset data-height=900}

### Method

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = method)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Method") + 
    facet_wrap(~printname)
)
```

### Tissue

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = tissue)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Tissue") + 
    facet_wrap(~printname)
)
```

### BMI

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = ifelse(is.na(bmi), bmi.baseline, bmi))) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "BMI") + 
    facet_wrap(~printname)
)
```

### Maternal age

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = age)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Maternal age") + 
    facet_wrap(~printname)
)
```

### Systolic blood pressure

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = systolic)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Systolic blood pressure") + 
    facet_wrap(~printname)
)
```

### Distolic blood pressure

```{r}
ggplotly(
  ggplot(merge(df_aggregated,cytokines),
         aes(ga, ifelse(grepl("log",unit), exp(value), value), color = diastolic)) + geom_point() + 
    theme_bw() + scale_y_log10() + theme(legend.position = "bottom") +
    labs(x = "Gestational age", y = "Concentration", color = "Distolic blood pressure") + 
    facet_wrap(~printname)
)
```

# Contribute {data-icon="fa-hands-helping"}

## Row

### How to contribute

Feel free to contribute! The easiest way to contribute is through [github](https://github.com/andjar/CyPreg) and is described step-wise below.

1.  If you are new to git, [this guide](https://www.dataschool.io/how-to-contribute-on-github/) can help you getting started. The repository for the database is `https://github.com/andjar/CyPreg.git`

2.  Check `data/studies.csv` (or the Overview page) to see that the study you want to add is missing from the database

3.  Add the new study to `data/studies.csv`. Here, `type` should be either `raw` or `aggregated`, and the preferred filename is of the form `firstauthorYYYY.csv` (e.g. `stokkeland2019.csv`)

4.  The data are to be added in a new .csv-file but it may be nice to use an existing file as template. Raw data live in the `data/raw` folder and aggregated data in `data/aggregated`.

5.  The data file should have a long format where each cytokine measurement has its own row. The variable names are columns with the variable name on top. Please see `data/variables.csv` for variable names

    -   If you want to append a new variable, you must also add it to `data/variables.csv` and provide a short description so that others can understand exactly what it means

    -   Please adhere to the following convention: Variable names should have the form `basename.suffix` where `basename` is added to `data/variable.csv`. Available suffixes, that are used in the csf files that contain data, are

        -   `median`: If the given value is reported as median

        -   `mean`: If the given value is reported as mean
        
        -   `sd`: If the variation in the given value is reported as standard deviation
        
        -   `percentile.%n`: If the variation in the given value is reported as the %nth percentile. Remember that range corresponds to the 0-100th percentile
        
        -   `def`: To provide details regarding a basevariable

    -   The highest and lower percentiles will be used for `basename.upper` and `basename.lower`, respectively. If standard deviation is given, upper and lower will be the corresponding value +/- 1.97 times the standard deviation

6.  Cytokine names should match the column `cytokine` in `data/cytokines.csv`